Matching Bullets

### 2015-12-07 imaging-paper.Rnw
Fix broken figure reference
random forest doesn't seem to help
land 1 of Bullet 1-1 exchanged for land 5

br111 <- read.x3p(paste(datadir,"Br1 Bullet 1-1.x3p", sep = "/"))
dbr111 <- fortify_x3p(br111)

@@

\begin{figure}[hbtp]
  \centering
<<circlefits, echo=FALSE, fig.width=7, fig.height=7, out.width='\\linewidth', warning=FALSE>>=
qplot(y, resid, data=subset(db2, x == 100), #colour=factor(x), 
      geom="line", size=I(1), colour=I("grey70")) + 
  facet_wrap(~part, ncol=2) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(aes(y, resid, group = x), colour="black", size=1, 
             data = filter(db1, part==1, x == 100)[,c("y", "resid", "x")]) +
  ylab("Residuals from circular fit") +
  ggtitle("Part 1 of Bullet 1 in black")
@
\caption{Circle fit for each cross section of bullet 2, with part 1 of bullet 1 overlaid.\label{fig:circlefits}}%
\end{figure}

@@

\begin{figure}
\begin{subfigure}[t]{\linewidth}
\caption{\label{fig:loess_step1}Step 1 the Loess fit algorithm. For a fixed crosscut (x held constant at 243.75) height values for part 1 of bullet 1 are plotted across different values of y.}
<<loess_step1, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\linewidth', warning=FALSE,  message=FALSE>>=
br111_bullet <- get_bullet(paste(datadir,"Br1 Bullet 1-1.x3p", sep = "/"))
br121_bullet <- get_bullet(paste(datadir,"Br1 Bullet 2-1.x3p", sep = "/"))
br122_bullet <- get_bullet(paste(datadir,"Br1 Bullet 2-2.x3p", sep = "/"))
br123_bullet <- get_bullet(paste(datadir,"Br1 Bullet 2-3.x3p", sep = "/"))
br124_bullet <- get_bullet(paste(datadir,"Br1 Bullet 2-4.x3p", sep = "/"))
br125_bullet <- get_bullet(paste(datadir,"Br1 Bullet 2-5.x3p", sep = "/"))
br126_bullet <- get_bullet(paste(datadir,"Br1 Bullet 2-6.x3p", sep = "/"))

@@

my.loess$fitted
@
\end{subfigure}
\begin{subfigure}[t]{\linewidth}
\caption{\label{fig:loess_resid} Residuals of Loess fit for land 1 of bullet 1.}
<<loess_resid, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\linewidth', warning=FALSE>>=
my.loess$resid
@
\end{subfigure}
\caption{Fit and residuals of a loess fit to land 1 of bullet 1 (Barrel 1).}
\end{figure}

@@

qplot(y, resid, data=melt.df, #colour=factor(x), 
      geom="line", size=I(1), colour=I("grey70")) + 
  facet_wrap(~part, ncol=2) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(data = actual.df, aes(y, resid), colour="black", size=1) + ggtitle("Land 1 of Bullet 1 in black")
@    
\caption{Residuals of a loess fit to bullets 1 and 2 from barrel 1. Land 1 of bullet 1 is shown in black. }
\end{figure}

@@

>>>>

br111 <- read.x3p(paste(datadir,"Br1 Bullet 1-5.x3p", sep = "/"))
dbr111 <- fortify_x3p(br111)

@@

\begin{figure}[hbtp]
  \centering
<<circlefits, echo=FALSE, fig.width=7, fig.height=7, out.width='\\linewidth', warning=FALSE>>=
qplot(y, resid, data=subset(db2, x == 100), #colour=factor(x), 
      geom="line", size=I(.75), colour=I("grey70")) + 
  facet_wrap(~part, ncol=2) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(aes(y, resid, group = x), colour="black", size=.75, alpha=0.5,
             data = filter(db1, part==5, x == 100)[,c("y", "resid", "x")]) +
  ylab("Residuals from circular fit") +
  ggtitle("Land 5 of Bullet 1 in black")
@
\caption{Circle fit for each cross section of bullet 2, with land 5 of bullet 1 overlaid.\label{fig:circlefits}}%
\end{figure}

@@

\begin{figure}
\begin{subfigure}[t]{\linewidth}
\caption{\label{fig:loess_step1}Step 1 the Loess fit algorithm. For a fixed crosscut (x held constant at 243.75) height values for part 1 of bullet 1 are plotted across different values of y.}
<<loess_step1, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\linewidth', warning=FALSE,  message=FALSE>>=
br111_bullet <- get_bullet(paste(datadir,"Br1 Bullet 1-5.x3p", sep = "/"))
br121_bullet <- get_bullet(paste(datadir,"Br1 Bullet 2-1.x3p", sep = "/"))
br122_bullet <- get_bullet(paste(datadir,"Br1 Bullet 2-2.x3p", sep = "/"))
br123_bullet <- get_bullet(paste(datadir,"Br1 Bullet 2-3.x3p", sep = "/"))
br124_bullet <- get_bullet(paste(datadir,"Br1 Bullet 2-4.x3p", sep = "/"))
br125_bullet <- get_bullet(paste(datadir,"Br1 Bullet 2-5.x3p", sep = "/"))
br126_bullet <- get_bullet(paste(datadir,"Br1 Bullet 2-6.x3p", sep = "/"))

@@

my.loess$fitted
@
\end{subfigure}
\begin{subfigure}[t]{\linewidth}
\caption{\label{fig:loess_resid} Residuals of Loess fit for land 1 of bullet 1.}
<<loess_resid, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\linewidth', warning=FALSE>>=
my.loess$resid + ylab("Residual of Loess Fit")
@
\end{subfigure}
\caption{Fit and residuals of a loess fit to land 5 of bullet 1 (Barrel 1).}
\end{figure}

@@

qplot(y, resid, data=melt.df, #colour=factor(x), 
      geom="line", size=I(.75), colour=I("grey70")) + 
  facet_wrap(~part, ncol=2) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(data = actual.df, aes(y, resid), colour="black", size=.75, alpha=0.5) + ggtitle("Land 5 of Bullet 1 in black")
@    
\caption{\label{fig:loessfits} Residuals of a loess fit to bullets 1 and 2 from barrel 1. Land 5 of bullet 1 is shown in black. }
\end{figure}

@@

%' 
%' <<rforest, echo=FALSE>>=
%' library(randomForest)
%' rtrees <- randomForest(factor(match)~., data=CCFs[,includes], ntree=1000)
%' CCFs$forest <- predict(rtrees)
%' importance(rtrees)
%' @
%'
